Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-06-18 manuscript_results.Rmd
code review up to line 2000
update

```{r}
# MAP 1 week ahead
W1_map <- data.frame(
  STATE = W1$STATE,
  percentage_improvement = W1_percentage_of_improvement$AUTO_AVG_LB,
  AUTO_AVG=W1$AUTO_AVG_LB
)

@@

# MAP 2 weeks a ahead
W2_map <- data.frame(
  STATE = W2$STATE,
  percentage_improvement = W2_percentage_of_improvement$AUTO_AVG_LB,
  AUTO_AVG=W2$AUTO_AVG_LB
)

@@

# MAP 3 weeks a ahead
W3_map <- data.frame(
  STATE = W3$STATE,
  percentage_improvement = W3_percentage_of_improvement$AUTO_AVG_LB,
  AUTO_AVG=W3$AUTO_AVG_LB
)

@@

# MAP 4 weeks ahead
W4_map <- data.frame(
  STATE = W4$STATE,
  percentage_improvement = W4_percentage_of_improvement$AUTO_AVG_LB,
  AUTO_AVG=W4$AUTO_AVG_LB
)

@@

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("1 week ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",  
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("2 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("3 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = AUTO_AVG)) +
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", 
                       midpoint = 100, limits = c(0, 352)) +  
  ggtitle("4 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(AUTO_AVG,0)),  
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +
  labs(
    fill = "mean WIS", 
       x = "",
       y = ""
  )

@@

@@

Percentage of AUTO_ADJ mean WIS

AUTO_ADJ WIS x RESIDENT POPULATION 2020

@@

  # Combining data for the same states
  WIS_pop_data <- inner_join(WIS_dataframes[[i]], pop_data, by = "STATE")
  # Fitting the regression model
  model <- lm((WIS_pop_data$AUTO_AVG) ~ (WIS_pop_data$Resident_population_2020))
  # View the model summary
  model_summary <- summary(model)
  # Getting the R and p values for the plot
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # Saving the results in a dataframe
  regression_models2 <- data.frame(
    independent_variable = "Resident Population (2020)", 
    Week_Ahead = i, 
    r_squared = r_squared, 
    p_value = p_value
  )
  # Append to the main results dataframe
  regression_models <- rbind(regression_models, regression_models2)
}

@@

  # Fit linear model
  model <- lm(AUTO_AVG ~ Resident_population_2020, data = WIS_pop_data)
  model_summary <- summary(model)

@@

  # Create plot
  p <- ggplot(WIS_pop_data, aes(x = Resident_population_2020, y = AUTO_AVG)) +
    geom_point(color = "steelblue", size = 2) +
    geom_smooth(method = "lm", se = FALSE, color = "darkred", linetype = "dashed") +
    labs(
      title = paste("Regression","Target Week", i),
      subtitle = paste("R² =", r_squared, "| p =", p_value),
      x = "Resident Population (2020)",
      y = "AUTO_AVG"
    ) +
    theme_minimal()

@@

  WIS_pop_data <- inner_join(WIS_dataframes[[i]], pop_data, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_pop_data$AUTO_AVG) ~ (WIS_pop_data$Population_density_2020))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="Population Density (2020)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # Append to the main results dataframe
  regression_models<-rbind(regression_models,regression_models2)
}

@@

  WIS_sovi<-NULL
  WIS_sovi <- inner_join(WIS_dataframes[[i]], sovi_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_sovi$AUTO_AVG) ~ (WIS_sovi$weighted_mean))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="Social Vulnerability Index (SoVI)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending the results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for(i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model  
  model <- lm((WIS_bric$AUTO_AVG) ~ (WIS_bric$weighted_mean_z_bric.social))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Social (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending the results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

```{r}
for(i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG) ~ (WIS_bric$weighted_mean_z_bric.economic))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Economic (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for (i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG) ~ (WIS_bric$weighted_mean_z_bric.infrastructure))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Infrastructure (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for (i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG) ~ (WIS_bric$weighted_mean_z_bric.institutional))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Institutional (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for(i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[1]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG) ~ (WIS_bric$weighted_mean_z_bric.community))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Community (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for(i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG) ~ (WIS_bric$weighted_mean_z_bric.environment))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Environment (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for(i in 1:4){
  # BRIC INDEX
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG) ~ (WIS_bric$weighted_mean_z_bric.total))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC total (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  regression_models<-rbind(regression_models,regression_models2)
}
```

@@

```{r}
for(i in 1:4){
  # TEMPERATURE DATA from ERA5
  WIS_temp <- inner_join(WIS_dataframes[[i]], temperature_data, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_temp$AUTO_AVG) ~ (WIS_temp$mean))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="Mean Temperature (1990-2020)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending results
  regression_models<-rbind(regression_models,regression_models2)
}
```

@@

for(i in 1:4){
  # HUMIDITY DATA from ERA5
  WIS_humidity <- inner_join(WIS_dataframes[[i]], humidity_data, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_humidity$AUTO_AVG) ~ (WIS_humidity$mean))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="Mean Specific Humidty (1990-2020)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

Let's plot some maps with the with the mean (%) of difference between the AUTO_AVG and the AUTO ARIMA models for the same state.

@@

AUTO_AVG WIS x RESIDENT POPULATION 2020

@@

AUTO_AVG WIS x POPULATION DENSITY

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

#ggsave(model_improv, height = 4.5, width = 9,  filename="Fig10.jpg")  
```
hospitalizations

@@

>>>>

```{r}
# MAP 1 week ahead
W1_map <- data.frame(
  STATE = W1$STATE,
  percentage_improvement = W1_percentage_of_improvement$AUTO_AVG_LB,
  AUTO_AVG_LB=W1$AUTO_AVG_LB
)

@@

# MAP 2 weeks a ahead
W2_map <- data.frame(
  STATE = W2$STATE,
  percentage_improvement = W2_percentage_of_improvement$AUTO_AVG_LB,
  AUTO_AVG_LB=W2$AUTO_AVG_LB
)

@@

# MAP 3 weeks a ahead
W3_map <- data.frame(
  STATE = W3$STATE,
  percentage_improvement = W3_percentage_of_improvement$AUTO_AVG_LB,
  AUTO_AVG_LB=W3$AUTO_AVG_LB
)

@@

# MAP 4 weeks ahead
W4_map <- data.frame(
  STATE = W4$STATE,
  percentage_improvement = W4_percentage_of_improvement$AUTO_AVG_LB,
  AUTO_AVG_LB=W4$AUTO_AVG_LB
)

@@

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = AUTO_AVG_LB)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("1 week ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(AUTO_AVG_LB,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",  
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = AUTO_AVG_LB)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("2 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(AUTO_AVG_LB,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = AUTO_AVG_LB)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("3 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(AUTO_AVG_LB,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = AUTO_AVG_LB)) +
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", 
                       midpoint = 100, limits = c(0, 352)) +  
  ggtitle("4 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(AUTO_AVG_LB,0)),  
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +
  labs(
    fill = "mean WIS", 
       x = "",
       y = ""
  )

@@

Now we run regressions models for evaluating if the best model mean WIS in each state is related to given independent variables.

@@

AUTO_ADJ_LB WIS x RESIDENT POPULATION 2020

@@

  # Combining data for the same states
  WIS_pop_data <- inner_join(WIS_dataframes[[i]], pop_data, by = "STATE")
  # Fitting the regression model
  model <- lm((WIS_pop_data$AUTO_AVG_LB) ~ (WIS_pop_data$Resident_population_2020))
  # View the model summary
  model_summary <- summary(model)
  # Getting the R and p values for the plot
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # Saving the results in a dataframe
  regression_models2 <- data.frame(
    independent_variable = "Resident Population (2020)", 
    Week_Ahead = i, 
    r_squared = r_squared, 
    p_value = p_value
  )
  # Append to the main results dataframe
  regression_models <- rbind(regression_models, regression_models2)
}

@@

  # Fit linear model
  model <- lm(AUTO_AVG_LB ~ Resident_population_2020, data = WIS_pop_data)
  model_summary <- summary(model)

@@

  # Create plot
  p <- ggplot(WIS_pop_data, aes(x = Resident_population_2020, y = AUTO_AVG_LB)) +
    geom_point(color = "steelblue", size = 2) +
    geom_smooth(method = "lm", se = FALSE, color = "darkred", linetype = "dashed") +
    labs(
      title = paste("Regression","Target Week", i),
      subtitle = paste("R² =", r_squared, "| p =", p_value),
      x = "Resident Population (2020)",
      y = "AUTO_AVG"
    ) +
    theme_minimal()

@@

  WIS_pop_data <- inner_join(WIS_dataframes[[i]], pop_data, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_pop_data$AUTO_AVG_LB) ~ (WIS_pop_data$Population_density_2020))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="Population Density (2020)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # Append to the main results dataframe
  regression_models<-rbind(regression_models,regression_models2)
}

@@

  WIS_sovi<-NULL
  WIS_sovi <- inner_join(WIS_dataframes[[i]], sovi_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_sovi$AUTO_AVG_LB) ~ (WIS_sovi$weighted_mean))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="Social Vulnerability Index (SoVI)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending the results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for(i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model  
  model <- lm((WIS_bric$AUTO_AVG_LB) ~ (WIS_bric$weighted_mean_z_bric.social))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Social (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending the results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

```{r}
for(i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG_LB) ~ (WIS_bric$weighted_mean_z_bric.economic))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Economic (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for (i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG_LB) ~ (WIS_bric$weighted_mean_z_bric.infrastructure))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Infrastructure (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for (i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG_LB) ~ (WIS_bric$weighted_mean_z_bric.institutional))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Institutional (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for(i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[1]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG_LB) ~ (WIS_bric$weighted_mean_z_bric.community))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Community (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for(i in 1:4){
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG_LB) ~ (WIS_bric$weighted_mean_z_bric.environment))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC Environment (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  regression_models<-rbind(regression_models,regression_models2)
}

@@

for(i in 1:4){
  # BRIC INDEX
  WIS_bric <- inner_join(WIS_dataframes[[i]], bric_by_state, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_bric$AUTO_AVG_LB) ~ (WIS_bric$weighted_mean_z_bric.total))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="BRIC total (2015)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  regression_models<-rbind(regression_models,regression_models2)
}
```

@@

```{r}
for(i in 1:4){
  # TEMPERATURE DATA from ERA5
  WIS_temp <- inner_join(WIS_dataframes[[i]], temperature_data, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_temp$AUTO_AVG_LB) ~ (WIS_temp$mean))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="Mean Temperature (1990-2020)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending results
  regression_models<-rbind(regression_models,regression_models2)
}
```

@@

for(i in 1:4){
  # HUMIDITY DATA from ERA5
  WIS_humidity <- inner_join(WIS_dataframes[[i]], humidity_data, by = "STATE")
  # Fit the regression model
  model <- lm((WIS_humidity$AUTO_AVG_LB) ~ (WIS_humidity$mean))
  # View the model summary
  model_summary <- summary(model)
  # Extract R-squared and p-value
  r_squared <- round(model_summary$r.squared, 3)
  p_value <- signif(model_summary$coefficients[2, 4], 3)
  # saving the results in a dataframe
  regression_models2<-data.frame("independent_variable"="Mean Specific Humidty (1990-2020)","Week_Ahead"=i, "r_squared"=r_squared,"p_value"= p_value)
  # appending results
  regression_models<-rbind(regression_models,regression_models2)
}

@@

Let's plot some maps with the with the mean difference (%) between the AUTO_AVG and the AUTO ARIMA models for the same state.

@@

AUTO_AVG_LB WIS x RESIDENT POPULATION 2020

@@

AUTO_AVG_LB WIS x POPULATION DENSITY

@@

AUTO_AVG_LB WIS x SOVI

@@

AUTO_AVG_LB WIS x BRIC SOCIAL

@@

AUTO_AVG_LB WIS x BRIC ECONOMIC

@@

AUTO_AVG_LB WIS x BRIC Infrastructure

@@

Plotting best regression model

@@

AUTO_AVG_LB WIS x BRIC institutional

@@

AUTO_AVG_LB WIS x BRIC community

@@

AUTO_AVG_LB WIS x BRIC environment

@@

AUTO_AVG_LB WIS x BRIC total

@@

AUTO_AVG_LB WIS x Temperature ERA5 Data

@@

AUTO_AVG_LB WIS x Specific Humidity ERA5 Data

@@

# Plot the table
regression_models
```
SUMMARY OF RESULTS

@@

Computing and plotting mean WIS improvement by epidemiological weeks.

@@

#ggsave(model_improv, height = 4.5, width = 9,  filename="Fig10.jpg")  
```
Total hospitalizations

@@

```
Combining model improvement and total hospitalizations
